---
title: "Booking.com European landscape analysis"
author: "Project Group 6"
date: "29/11/2020"
output: html_document
---
###Loading Packages
```{r}
library(ggplot2)
library(janitor)
library(tidyverse)
library(caret)
library(lubridate)
library(factoextra)
library(vroom)
library(Hmisc)
library(mice)
library(readxl)
library(skimr)
library(data.table)
library(grid)
library(pBrackets)
library(showtext)
font_add_google("Montserrat", "Montserrat") #downloading fonts from Google
showtext_auto()
library(data.table)
library(googlesheets4)
library(opencage)

```


###Importing the Data Set
```{r setup, include=FALSE}
hotels_raw<-vroom("Hotel_Reviews 2.csv") %>% clean_names()

global_hotel_chain_size <- read_excel("Global Hotel Chains Size.xlsx") %>%clean_names()
                                      
booking_satisfaction <- vroom("Europe Hotel Booking Satisfaction Score.csv")%>%clean_names()

country_continent <- vroom("continents2.csv")%>%clean_names()

```
# Story Time

 We are a group of individuals working within the Data Analytics Team at Booking.com, and have been asked to gather insights on the mid- to high-end (luxury) hotel market in Europe. We are to present our results to our Team Lead.
 
  
# Cleaning Data Set global_hotel_chain_sizec
First, let's have a look at the overall global luxury & upscale hotel market. 
```{r}
# let's have a look on our data set
describe(global_hotel_chain_size) 

#Remove empty columns and rows
global_hotel_chain_size_clean<-remove_empty(global_hotel_chain_size, which = c("rows","cols"))


describe(global_hotel_chain_size_clean) 

```



